True versus apparent shapes of bow shocks

### 2018-03-07 papers/Papers1234/sec-projection.tex
Add references to Wilkin thesis and to Ng

Note that equation~(\ref{eq:tanphi}) will not have a solution for
arbitrary values of $\theta$ and $i$, but only when
$|\tan i\tan\alpha|<1$. In particular, if $i\neq 0$, then the tangent line
only exists for \(\theta > \theta_{0}\) where \(\theta_{0}\) is the value of
\(\theta\) on the tangent line's projected symmetry axis
(\(\theta' = 0\)).  From equations~(\ref{eq:tangential},
\ref{eq:R-prime-theta-prime}) it follows that \(\sin^2\phi\T = 1\) at
\(\theta = \theta_0\), which yields the implicit equation
\begin{align}
\tan\theta_{0} = \frac{|\tan i| + \omega(\theta_{0})}{1-\omega(\theta_{0}) |\tan i|} . 
\label{eq:thetapar}
\end{align}
In addition, if the surface is sufficiently ``open''
(\(\alpha \ge \alpha_{\mathrm{min}} > 0\) for all \(\theta\)), then for those
inclinations with
\(\vert i\vert > (\ang{90} - \alpha_{\mathrm{min}}) \) the tangent line does not exist
for any value of \(\theta\).  In other words, when the viewing angle is
sufficiently close to face-on, the projected surface has no ``edge''
and will no longer look like a bow shock to the observer.

>>>>

Equation~(\ref{eq:tanphi}) will not have a solution for
arbitrary values of $\theta$ and $i$, but only when
$|\tan i\tan\alpha|<1$. In particular, if $i\neq 0$, then the tangent line
only exists for \(\theta > \theta_{0}\) where \(\theta_{0}\) is the value of
\(\theta\) on the tangent line's projected symmetry axis
(\(\theta' = 0\)).  From equations~(\ref{eq:tangential},
\ref{eq:R-prime-theta-prime}) it follows that \(\sin^2\phi\T = 1\) at
\(\theta = \theta_0\), which yields the implicit equation
\begin{align}
\tan\theta_{0} = \frac{|\tan i| + \omega(\theta_{0})}{1-\omega(\theta_{0}) |\tan i|} . 
\label{eq:thetapar}
\end{align}
In addition, if the surface is sufficiently ``open''
(\(\alpha \ge \alpha_{\mathrm{min}} > 0\) for all \(\theta\)), then for those
inclinations with
\(\vert i\vert > (\ang{90} - \alpha_{\mathrm{min}}) \) the tangent line does not exist
for any value of \(\theta\).  In other words, when the viewing angle is
sufficiently close to face-on, the projected surface has no ``edge''
and will no longer look like a bow shock to the observer.

After completing this work, it was brought to our attention that the
principal results of this section had already been derived in
Appendix~B of the PhD thesis \citet{Wilkin:1997a}.  For instance,
Wilkin's equation~(8) is equivalent (apart from differences in
notation) to our equation~\eqref{eq:tanphi}.

### 2018-03-07 papers/Papers1234/sec-thin-shell.tex
Add references to Wilkin thesis and to Ng

Figures~\ref{fig:xyprime} and~\ref{fig:xyprime-ancantoid} show the
apparent bow shapes of various thin shell models (wilkinoid, cantoids,
ancantoids) for different inclination angles \(\abs{i}\).  For
comparison, Figure~\ref{fig:xyprime}a shows the confocal paraboloid,
whose apparent shape is independent of inclination (see
Appendix~\ref{app:parabola}).  The wilkinoid (Fig.~\ref{fig:xyprime}b)
shows only subtle changes, with the wings becoming slightly more swept
back as the inclination increases.  The cantoids
(Fig.~\ref{fig:xyprime}c and d) behave in the opposite way, with the
wings becoming markedly more open once \(\abs{i}\) exceeds
\(\ang{60}\) (for \(\beta = 0.001\)), or \(\ang{45}\) (for
\(\beta = 0.01\)).  The ancantoids (Fig.~\ref{fig:xyprime-ancantoid}) can
show more complex behavior.  For instance, in the \(k = 0.5\),
\(\beta = 0.001\) ancantoid (Fig.~\ref{fig:xyprime-ancantoid}a) the near
wings begin to become more closed with increasing inclination up to
\(\abs{i} = \ang{60}\), at which point they open up again, whereas the
opening angle of the far wings increases monotonically with
\(\abs{i}\).

>>>>

Figures~\ref{fig:xyprime} and~\ref{fig:xyprime-ancantoid} show the
apparent bow shapes of various thin shell models (wilkinoid, cantoids,
ancantoids)\footnote{%
  See also previous studies of the projected shape of the wilkinoid
  \citep{Wilkin:1997a, Cox:2012a, Ng:2017a} and the cantoids
  \citep{Robberto:2005a}.} %
for different inclination angles \(\abs{i}\).  For comparison,
Figure~\ref{fig:xyprime}a shows the confocal paraboloid, whose
apparent shape is independent of inclination (see
Appendix~\ref{app:parabola}).  The wilkinoid (Fig.~\ref{fig:xyprime}b)
shows only subtle changes, with the wings becoming slightly more swept
back as the inclination increases.  The cantoids
(Fig.~\ref{fig:xyprime}c and d) behave in the opposite way, with the
wings becoming markedly more open once \(\abs{i}\) exceeds
\(\ang{60}\) (for \(\beta = 0.001\)), or \(\ang{45}\) (for
\(\beta = 0.01\)).  The ancantoids (Fig.~\ref{fig:xyprime-ancantoid}) can
show more complex behavior.  For instance, in the \(k = 0.5\),
\(\beta = 0.001\) ancantoid (Fig.~\ref{fig:xyprime-ancantoid}a) the near
wings begin to become more closed with increasing inclination up to
\(\abs{i} = \ang{60}\), at which point they open up again, whereas the
opening angle of the far wings increases monotonically with
\(\abs{i}\).

### 2018-03-07 papers/paper1-submit/latexdiff/ms-bows02-expand.tex
Add references to Wilkin thesis and to Ng

Several previous studies have discussed the relation between
\(R_{90}\) and \(R_0\) as a diagnostic of bow shape (for example
\citealp{Robberto:2005, Cox:2012a, Meyer:2016a}), but as far as we
know, we are the first to include \(R_{\C}\).  \citet{Robberto:2005}
\S~4.2 use the ratios \(R_0/D\) and \(R_{90}/D\) in analyzing proplyd
bow shapes in the Trapezium cluster in the center of the Orion Nebula
\citep{Hayward:1994a, Garcia-Arredondo:2001a, Smith:2005a}.  In that
case, the source of the outer wind is known, and so \(D\) is
well-determined (at least, in projection), but for many bow shocks
\(D\) is not known, and is not even defined for the moving-star or
parallel-stream case. \citet{Cox:2012a} \S~4.1 compare the observed
shapes of bow shocks around cool giant stars with an analytic model,
and use \(A\) and \(B\) for the projected values of \(R_0\) and
\(R_{90}\), respectively (see next section for discussion of
projection effects).  \citet{Meyer:2016a} \S~3.2 analyze the
distribution of \(R_0 / R_{90}\) (the reciprocal of our \(\Lambda\)) for
hydrodynamic simulations of bow shocks around runaway OB stars.

@@

@@

\bibitem[\protect\citeauthoryear{{Robberto} et~al.,}{{Robberto}
  et~al.}{2005}]{Robberto:2005}
{Robberto} M.,  et~al., 2005, \mn@doi [\aj] {10.1086/428000}, \href
  {http://adsabs.harvard.edu/abs/2005AJ....129.1534R} {129, 1534}

@@

>>>>

Several previous studies have discussed the relation between
\(R_{90}\) and \(R_0\) as a diagnostic of bow shape (for example
\citealp{Robberto:2005a, Cox:2012a, Meyer:2016a}), but as far as we
know, we are the first to include \(R_{\C}\).  \citet{Robberto:2005a}
\S~4.2 use the ratios \(R_0/D\) and \(R_{90}/D\) in analyzing proplyd
bow shapes in the Trapezium cluster in the center of the Orion Nebula
\citep{Hayward:1994a, Garcia-Arredondo:2001a, Smith:2005a}.  In that
case, the source of the outer wind is known, and so \(D\) is
well-determined (at least, in projection), but for many bow shocks
\(D\) is not known, and is not even defined for the moving-star or
parallel-stream case. \citet{Cox:2012a} \S~4.1 compare the observed
shapes of bow shocks around cool giant stars with an analytic model,
and use \(A\) and \(B\) for the projected values of \(R_0\) and
\(R_{90}\), respectively (see next section for discussion of
projection effects).  \citet{Meyer:2016a} \S~3.2 analyze the
distribution of \(R_0 / R_{90}\) (the reciprocal of our \(\Lambda\)) for
hydrodynamic simulations of bow shocks around runaway OB stars.

@@

\bibitem[\protect\citeauthoryear{{Ng}, {Bandiera}, {Hunstead}  \&
  {Johnston}}{{Ng} et~al.}{2017}]{Ng:2017a}
{Ng} C.-Y.,  {Bandiera} R.,  {Hunstead} R.~W.,   {Johnston} S.,  2017, \apj,
  842, 100

@@

\bibitem[\protect\citeauthoryear{{Robberto} et~al.,}{{Robberto}
  et~al.}{2005}]{Robberto:2005a}
{Robberto} M.,  et~al., 2005, \aj, 129, 1534

@@

\bibitem[\protect\citeauthoryear{{Wilkin}}{{Wilkin}}{1997}]{Wilkin:1997a}
{Wilkin} F.~P.,  1997, PhD thesis, University of California, Berkeley
